A Global Genome-wide Scan with Optimal Cutoff Mining for Emerging Biomarkers in Head and Neck Squamous Cell Carcinoma

### 2021-02-09 revisionNotel2_responses.tex
Alex’s approval: done (our laboratory)

\subsection*{Revision notes: rebuttal}  
%Where the authors disagree with a reviewer, they must provide a clear response by a rebuttal if some of the reviewer’s comments cannot be revised. 
%動之以情，和氣誠懇地說明原委 https://www.mdpi.com/journal/cancers/instructions#editorial_procedure
% *** Alex: yes, please answer the reviewer politely 和氣誠懇地 and tell him that 
%in a respectful and considerate manner.
We appreciate the reviewer for the critical comment and apology for short of experiment results. 
%We modified "Material and Methods",  Results and Discussion of manuscript according the new evidence.
It is encouraged for multidisciplinary studies that use complementary computational and experimental approaches to address challenging cancer research.
%下一篇文章的內容。目前在計畫中，但還沒有開始進行
These in vitro and in vivo validation experiments will be undertaken in Alex's laboratory (one of our co-authors).
We plan to analyze mRNA (e.x. qRT-PCR) and protein (e.x. western blot) of HNSCC cell lysate to confirm the candidate genes' expression.
%mRNA expression level in HNSCC cell lines (其他文章已有發表 overexpression）
The effect of over-expression and knockdown of the gene by lentiviral clones should be observed on cell function assay (e.x. proliferation, migration, and invasion) and mouse xenograft model (e.x. tumor growth). %這些都需要一年以上的時間
%their rationale for looking into TMSB4X is not strongly supported by the available data.

@@

Once Alex's laboratory and the community identify those candidates as the targets, the compound screening could facilitate more individualized therapy for HNSCC patients and improve prognosis. %help to discover a potential drug for HNSCC therapy.
%https://www.mdpi.com/journal/cancers/instructions

>>>>

\subsection*{Revision notes: rebuttal}  
%Where the authors disagree with a reviewer, they must provide a clear response by a rebuttal if some of the reviewer’s comments cannot be revised. 
%動之以情，和氣誠懇地說明原委 https://www.mdpi.com/journal/cancers/instructions#editorial_procedure
% *** Alex: yes, please answer the reviewer politely 和氣誠懇地 and tell him that 
%in a respectful and considerate manner.
We appreciate the reviewer for the critical comment and apology for short of experiment results. 
%We modified "Material and Methods",  Results and Discussion of manuscript according the new evidence.
It is encouraged for multidisciplinary studies that use complementary computational and experimental approaches to address challenging cancer research.
%下一篇文章的內容。目前在計畫中，但還沒有開始進行
These in vitro and in vivo validation experiments will be undertaken in our laboratory.
We plan to analyze mRNA (e.x. qRT-PCR) and protein (e.x. western blot) of HNSCC cell lysate to confirm the candidate genes' expression.
%mRNA expression level in HNSCC cell lines (其他文章已有發表 overexpression）
The effect of over-expression and knockdown of the gene by lentiviral clones should be observed on cell function assay (e.x. proliferation, migration, and invasion) and mouse xenograft model (e.x. tumor growth). %這些都需要一年以上的時間
%their rationale for looking into TMSB4X is not strongly supported by the available data.

@@

Once our laboratory and the community identify those candidates as the targets, the compound screening could facilitate more individualized therapy for HNSCC patients and improve prognosis. %help to discover a potential drug for HNSCC therapy.
%https://www.mdpi.com/journal/cancers/instructions
